---
title: "Swirl_Course_Practise"
author: "Rahul"
date: "October 13, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Sequence of numbers
-- --

1. Creating Sequences in R

  + use " : " operator, from ith : to Jth number.
  
  + This gices us every integer b/w (and including) 1 and 20.
  
  + Can also create sequence of "Real numbers".
  
  
```{r}
# Create a sequence of numbers from 1:20

1:20

# Create a sequence of "Real numbers"
pi : 10

# With a little ingenuity we can create reverse sequence
15:1

# We can get more information about even the operators in R
#(uncomment to test these) ?`:` 
#(uncomment to test these) ?":"

```

-- --

2. Often we desire more control over a sequence we're creating, We could use the _seq()_ to do this.

  + To generate a sequence of _vectors of numbers_ to a range.
  
  + We can increment them using a _step size_ (say 0.5), to do this, we use _by_ statement.
  
  + We can be lazy too, we just want a sequence of n numbers b/w ith to jth no, we can use _length =_ argument and assign a integer value, denoting length of the sequence.
  
```{R}
seq(1, 20)

# create a vector of no. ranging from 0 to 10, step size of 0.5
seq(0, 10, by = 0.5)

# Create a sequence of 30 no's from 5 to 10
my_seq <- seq(5 , 10, length = 30)

# Try confirming if the length of "my_seq" is truely 30
length(my_seq)

# Using a bit of ingenuity we can also generate a vector( 1 to N) having the same length of my_seq if we don't know the length of my_seq
1:length(my_seq)

# and another way!
seq(along.with = my_seq)

# and yet another way!
seq_along( my_seq )



```